Study 1

### 2022-01-08 code/analysis.Rmd
2x2 analysis

d.round_results %>% filter(gameId=="KxJzRQeo5HikZxreo") %>% select(repNum, time, playerId) %>% arrange(time)
d.round_results <- read_csv(here(data_location,"raw_results.csv"))

@@

ggplot(summary, aes(x=str_c(game_cond," ", chat_cond), y=total_time, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+
  labs(title="Game time in min", y="mins", x="condition")+theme(legend.position = "none")
```

@@

Note that bonuses are not directly comparable between BoS & PD! 
But it looks like chat helps in BoS and not in PD.

@@

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```

@@

@@

# What do people choose

@@

In PD:

```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role) %>% 
  pivot_wider(names_from=role, values_from=response) %>% 
  mutate(outcome=str_c(p1,p2))

ggplot(outcome, aes(x=repNum, y=outcome, color=gameId))+geom_jitter(height=.1)+facet_wrap(.~gameId)

@@

```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role)

ggplot(outcome, aes(x=role, fill=response))+geom_bar(position="dodge")+facet_wrap(.~gameId)

>>>>

d.round_results <- read_csv(here(data_location,"raw_results.csv"))

@@

ggplot(summary, aes(x=str_c(game_cond," ", chat_cond), y=total_time, color=str_c(game_cond," ", chat_cond)))+geom_jitter(width=.1)+  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5,color="black")+
  labs(title="Game time in min", y="mins", x="condition")+theme(legend.position = "none")

summary %>% group_by(game_cond, chat_cond) %>% tally()
```
A respectable rate of game completion.

@@

Note that bonuses are not directly comparable between BoS & PD! 
But it looks like chat helps in BoS and not (much?) in PD.

@@

ggplot(chat, aes(x=str_c(game_cond," ", chat_cond), y=words))+geom_jitter(width=.1)+
  labs(title="Words produced in pre-chat", y="words", x="condition")
```
People talked some. I haven't looked at the transcripts at all.

@@

# Does chat help?

@@

## Choices

@@

In PD: P1 prefers BA > AA > BB > AB and P2 prefers AB > AA > BB > BA. (BB is Nash equilibrium, AA is Pareto dominant.)

Not really sure how to visualize this efficiently?

Being in the chat condition v not

```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role, game_cond, chat_cond) %>% 
  pivot_wider(names_from=role, values_from=response) %>% 
  mutate(outcome=str_c(p1,p2))

ggplot(outcome, aes(x=repNum, y=outcome))+geom_jitter(width=.1, alpha=.25)+facet_grid(game_cond~chat_cond)+theme(legend.position="none")

outcome_summary <- outcome %>% group_by(game_cond, chat_cond, repNum,outcome) %>% tally() %>% group_by(game_cond, chat_cond, repNum) %>% summarize(pct=n/sum(n), outcome=outcome)

ggplot(outcome_summary, aes(x=repNum, y=pct, color=chat_cond))+geom_line()+facet_grid(game_cond~outcome)

@@

Actually using the chat that round

```{r}
outcome <- d.round_results %>% select(gameId:repNum, response,role, game_cond, chat_cond) %>% 
  pivot_wider(names_from=role, values_from=response) %>% 
  mutate(outcome=str_c(p1,p2)) %>% filter(chat_cond=="chat") %>% left_join(chat_by_game) %>% mutate(is.chat=ifelse(words>0, 1,0))

outcome_summary <- outcome %>% group_by(game_cond, is.chat, repNum,outcome) %>% tally() %>% group_by(game_cond, is.chat, repNum) %>% summarize(pct=n/sum(n), outcome=outcome)

ggplot(outcome_summary, aes(x=repNum, y=pct, color=as.factor(is.chat)))+geom_line()+facet_grid(game_cond~outcome)
